---
title: "Introduction to R"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R
R is a system for statistical analyses and graphics, comparing to Matlab and SAS, R language is a free software. Therefore, R language has a wider user community at this stage.

R has many functions for statistical analyses and graphics; the latter are
visualized immediately in their own window and can be saved in various formats (jpg, png, bmp, ps, pdf, emf, pictex, xfig; the available formats may depend on the operating system).

## Calculation
You can use R to calculate complex calculations easily.

For example:
```{r}
a <- 16
b <- 3

add <- a + b
print(add)
sub = a - b
print(sub)
multi = a * b
print(multi)
division = a / b
print(division)
Integer_Division = a %/% b
print(Integer_Division)
exponent = a ^ b
print(exponent)
modulus = a %% b
print(modulus)


```

## Approximated values
```{r}
round(125.78253)
round(125.78253, digits = 3)
round(125.78253, digits = -2)
signif(125.78253, digits = 2)
floor(125.78253)
ceiling(125.78253)
trunc(125.78253)
```

## Descriptive statistics
```{r}
x <- 1:25
mean(x)
var(x)
median(x)
quantile(x, c(0.1, 0.5, 0.7))
```

## Creat a vector
We use c() to be a collection of needed values.
```{r}
x <- c(1, 3, 5, 7, 9, 11)
y <- c(2, 4, 6, 8, 10, 12)
x
y
```


## Assign values into a vector
```{r}
Xvector <- rep(NA, 6)
Xvector[3] <- 12
Xvector[c(4:6)] <- rep(1, 3)
Xvector
```

## Create a matrix
A matrix is a generalization containing multiple vectors.
```{r}
a <- 1:5; b <- 6:10;
c <- 11:15; d <- 16:20;
M1 <- rbind(a, b, c, d)
M1
M2 <- cbind(a, b, c, d)
M2
```

### Constrict a matrix by a long vector.
```{r}
X <- 1:20
matrix(X, nrow = 4, ncol = 5)
matrix(X, nrow = 5, ncol = 4)
matrix(X, nrow = 4, ncol = 5, byrow = TRUE)
matrix(X, nrow = 5, ncol = 4, byrow = TRUE)
```
## Indent style
There is two style you can choose.

* unordered list
* item 2
  + sub-item 1
  +sub 2

1. unordered list
2. item 2
   a. sub-item 1
   b. sub 2

## Create a form
Table Header | Second Header
-------------| -------------
Table Cell   | Cell 2
Cell 3       | Cell 4

Note:make sure your ilne in the code is alignment.

## Loop

Prefect number
```{r}
n <-100
perfect.function <- function(n){
  k <- 1
  while(k < n){
    fac <- c()
    for(j in 1:k){
      if((k %% j) == 0){
        fac <- c(fac, j)
      }
    }
    if(k == sum(fac[-length(fac)])){
      cat(paste(k, "=", sep=" "),
          paste(fac[-length(fac)], collapse = " + "), "\n")
    }
    k <- k+1
  }
}
perfect.function(n)
```


### Randomness
Rolling a fair dice, evaluate the total number that all possible
outcomes occur at least once. Start from the seed 20191025. Use
sample(1:6, 1) to simulate a outcome of rolling a fair dice.

```{r}
set.seed(20191025)
a <- c()
for (i in 1:100) {
  a <- c(a,runif(1))
  if(sum(a)>3){
    print(i)
    break
  }
}
```

## Statistics graphic

Using R to draw statistics grahics.
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot,so you can decide if you want to show your code to everyone.

The grahic below, I delete the `ehco=False` so you will see my code. 
For example:

```{r}
x <- 0:10
probablity <- dbinom(x, size=10, prob=0.7) 
plot  (x, probablity, type='h', ylab="pmf", cex.main=0.8, ylim = c(0, 0.4))
points(x, probablity, pch=19)
title(expression(paste("Binomial(n,p) with n =10")))
legend("topright", c("p = 0.7", "p = 0.5", "p = 0.2"), col=c("black","blue","red"), lty=c(1,4,2), pch=c(19,8,17))
par(new=TRUE)

probablity <- dbinom(x, size=10, prob=0.5)
plot  (x, probablity, col='blue', type='h', lty=4, xlab="", ylab="", ylim = c(0, 0.4))
points(x, probablity, pch=8, col='blue')
par(new=TRUE)

probablity <- dbinom(x, size=10, prob=0.2)
plot  (x, probablity, col='red', type='h', lty=2, xlab="", ylab="", ylim = c(0, 0.4))
points(x, probablity, pch=17, col='red')


```


