---
title: "Introduction to R"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R
R is a system for statistical analyses and graphics, comparing to Matlab and SAS, R language is a free software. Therefore, R language has a wider user community at this stage.

R has many functions for statistical analyses and graphics; the latter are
visualized immediately in their own window and can be saved in various formats (jpg, png, bmp, ps, pdf, emf, pictex, xfig; the available formats may depend on the operating system).



## Statistics graphic

Using R to draw statistics grahics.
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot,so you can decide if you want to show your code to everyone.

The grahic below, I delete the `ehco=False` so you will see my code. 
For example:

```{r}
x <- 0:10
probablity <- dbinom(x, size=10, prob=0.7) 
plot  (x, probablity, type='h', ylab="pmf", cex.main=0.8, ylim = c(0, 0.4))
points(x, probablity, pch=19)
title(expression(paste("Binomial(n,p) with n =10")))
legend("topright", c("p = 0.7", "p = 0.5", "p = 0.2"), col=c("black","blue","red"), lty=c(1,4,2), pch=c(19,8,17))
par(new=TRUE)

probablity <- dbinom(x, size=10, prob=0.5)
plot  (x, probablity, col='blue', type='h', lty=4, xlab="", ylab="", ylim = c(0, 0.4))
points(x, probablity, pch=8, col='blue')
par(new=TRUE)

probablity <- dbinom(x, size=10, prob=0.2)
plot  (x, probablity, col='red', type='h', lty=2, xlab="", ylab="", ylim = c(0, 0.4))
points(x, probablity, pch=17, col='red')


```


